%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Conference Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

%---------------------------------------------------------
    Bradford, I., Andersen, D., \textbf{Myers, G.M., } Rockson, P. 2023. “Comparison and Evaluation of SLAKEs and Cornell Aggregate Stability Test." American Society of Agricultural and Biological Engineers Annual International Meeting.” Omaha, Nebraska. July 9-12, 2023. Poster. 

    \textbf{Myers, G.M., }Raman, D.R.,  Andersen D.S., Moore, K.J., Peckinovsky, K.T. 2023. “Yield, soil, and water quality implications of conventional, cover-cropped, and perennial groundcover corn production systems in tile-drained Iowa cropland." American Society of Agricultural and Biological Engineers Annual International Meeting.” Omaha, Nebraska. July 9-12, 2023. Oral Presentation. \color{awesome}\textit{Presentation Excellence Award.}\color{darktext}
 
    \textbf{Myers, G.M., }Raman, D.R.,  Andersen D.S., Moore, K.J., Dougherty, B.W., Pedersen, C.H., Hintz, R.L., Peckinovsky, K.T. 2022. “Can perennial groundcover (PGC) decrease nutrient export through subsurface drainage without negatively impacting corn yields?" Iowa State College of Engineering Advisory Board Meeting. Ames, Iowa. May 10, 2023. Poster. 

    \textbf{Myers, G.M., }Andersen, D.S., Martens, B.J., Raman, D.R. 2023. “Cost Assessment of Centralizing a Swine Manure and Corn Stover Co-Digestion System.” Iowa State Agricultural Engineering In-Service. Ames, Iowa. May 9, 2023. Oral Presentation.
    
   \textbf{Myers, G.M., }Raman, D.R.,  Andersen D.S., Moore, K.J. 2023. “Yield and Drainage Water Quality Impacts of Agricultural Management Practices.” Iowa Pork Congress. Des Moines, Iowa. January 25-26, 2023. Poster. \color{awesome}\textit{Producers' Choice Award.} \color{darktext}
   
   \textbf{Myers, G.M., }Raman, D.R.,  Andersen D.S., Moore, K.J., Dougherty, B.W., Pedersen, C.H., Hintz, R.L., Peckinovsky, K.T. 2022. “Can perennial groundcover (PGC) decrease nutrient export through subsurface drainage without negatively impacting corn yields?" 2023 DataFEWSion Symposium. Ames, Iowa. January 10, 2023. Poster. 

    \textbf{Myers, G.M., }Raman, D.R., Andersen D.S., 2022. “Can we improve soil and water quality in the Corn Belt with Perennial Groundcover?” Integrated Crop Management Conference. Ames, Iowa. November 30-December 1, 2022. Infographic.
   
  \textbf{Myers, G.M., }Raman, D.R.,  Andersen D.S., Moore, K.J., Dougherty, B.W., Pedersen, C.H., Hintz, R.L., Peckinovsky, K.T. 2022. “First year outcomes of field trials to evaluate N export from perennial groundcover corn systems.” Iowa Water Conference. Dubuque, Iowa. September 28-29, 2022. Poster.

  \textbf{Myers, G.M., }Andersen, D.S., Raman, D.R. 2022. “Cost Assessment of Centralizing a Swine Manure and Corn Stover Co-Digestion System.” American Society of Agricultural and Biological Engineers Annual International Meeting. Houston, Texas. July 17-20, 2022. Poster. \color{awesome}\textit{Student Poster Award.}\color{darktext}

  \textbf{Myers, G.M., }Raman, D.R.,  Andersen D.S., Moore, K.J., Dougherty, B.W., Pedersen, C.H., Hintz, R.L., Peckinovsky, K.T. 2022. “First year outcomes of a perennial groundcover corn system. American Society of Agricultural and Biological Engineers Annual International Meeting.” Houston, Texas. July 17-20, 2022. Oral Presentation.

  \textbf{Myers, G.M., }Raman, D.R.,  Andersen D.S. 2022. “Technoeconomic analysis finds centralized swine manure and corn stover co-digestion systems have an economic advantage over distributed Systems.” 2022 DataFEWSion Symposium. January 11, 2022. Poster.

  \textbf{Myers, G.M., }Raman, D.R.,  Andersen D.S. 2021. “Carbon Balance for Conventional and Cell-Cultured Meat Production.” American Society of Agricultural and Biological Engineers Annual International Meeting. Virtual Meeting. July 12-16, 2021. Oral Presentation.

  \textbf{Myers, G.M., }Andersen D.S., Raman, D.R. 2021. “A Cost Assessment of Centralizing a Co-Digestion System for Biogas Production.” American Society of Agricultural and Biological Engineers Annual International Meeting. Virtual Meeting. July 12-16, 2021. Oral Presentation.

  \textbf{Myers, G.M., }Andersen, D.S., Raman D.R. 2020. “Biogas Production Cost Model.” C-Change Conference: Why are we missing the boat on biogas? Virtual meeting, Oct. 19, 2020. Oral Presentation.

  


%---------------------------------------------------------
\end{cvparagraph}