%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------



\begin{cvparagraph}

%---------------------------------------------------------
\cvsubsection{Peer Reviewed}
   
   \textbf{Myers, G.M., }Jaros, K.A., Andersen, D.S.,  \& Raman, D.R. 2023.Nutrient recovery in cultured meat systems: Impacts on cost and sustainability metrics. \textit{Frontiers in Nutrition,} 10. \url{https://doi.org/10.3389/fnut.2023.1151801}
   
   \textbf{Myers, G.M., }Andersen, D.S., Martens, B.J., \& Raman, D.R. 2023. Cost assessment of centralizing swine manure and corn stover co-digestion systems. \textit{Energies, 16}(11), 4315. \url{https://doi.org/10.3390/en16114315}

\cvsubsection{Reports}

   \textbf{Myers, G., }Dougherty, B., Pedersen, C., Andersen, D., Peckinovsky, K., Raman, D., Moore, K., \& Helmers, M. 2021 and 2022 Drainage Water Quality Impacts of Agricultural Management Practices. 2023. Farm Progress Report. \url{https://www.iastatedigitalpress.com/farmreports/article/id/16218/}

   Dougherty, B., \textbf{Myers, G., }Pedersen, C., Andersen, D., Helmers, M., Raman, D. R., \&  Moore, K. Effect of Annual and Perennial Cover Crops and Manure Application Timing on Yields in 2021. 2022. Farm Progress Report. \url{https://www.iastatedigitalpress.com/farmreports/article/id/15562/}

\cvsubsection{Conference Proceedings}

   \textbf{Myers, G.M., }Andersen, D.S.,  \& Raman, D.R. 2022. Cost assessment of centralizing a swine manure and corn stover co-digestion system for biogas production. 2021 ASABE Annual International Virtual Meeting, July 12-16, 2021. Conference Paper. doi:10.13031/aim.202100888


%---------------------------------------------------------
\end{cvparagraph}
